Appendix: New and simplified manual controls for projection and slice tours

### 2022-09-22 paper/appendix.Rmd
Some work on the appendix

A small modification to algorithm 1 will maintain the components of $V_m$ precisely (Figure \ref{fig:othermethod}. It is as follows:

@@

$$a^{**}_{j2}+\frac{a_{m1}a_{m2}}{p-1}, j=1, ..., p, j\neq m$$.

@@

$$\sum_{j=1, j\neq m}^p a^{**}_{j1}a^{**}_{j2} + a_{m1}a_{m2} = 0$$.

@@

For $d=2$ projections, the projection matrix is the sub-matrix of $A$ formed by its first two columns. Whereas orthonormality of the basis for the p-dimensional space is given by $e_i\cdot e_j=\delta_{ij},{i,j,=1,\cdots,}$, orthonormality of the projection matrix is expressed as $P_i\cdot P_j=\delta_{ij}, {i,j=1,2}$. Movement of the cursor takes the two components ${x_{m1},x_{m2}}$ into a selected new value ${a,b}$. Although the motion is constrained by $a^2+b^2\leq 1$, this is not sufficient to guarantee orthonormality of the new projection matrix. One possible algorithm to achieve this is
\begin{enumerate}
\item Cursor movement takes ${x_{m1},x_{m2}}\to {a,b}$
\item The freedom to change the components $A_{i3}\cdots A_{ip}$ (the columns of $A$ not corresponding to the projection matrix) is used to select a new orthonormal basis as follows:
\begin{enumerate}
\item For row $m$ one chooses $A_{m3}=\sqrt{1-a^2-b^2},~A_{m,k>3}=0$
\item For other rows, $A_{i\neq m,j\geq3}$ random selections in the range $(-1,1)$ are made.
\item The Gram-Schmidt algorithm is then used to obtain an orthonormal basis taking $e_m$ as the first vector (which is already normalized), and then proceeding as usual $e_1\to e_1-(e_1\cdot e_m) e_m$, $e_1\to e_1/(e_1\cdot e_1)$, etc.
\end{enumerate}
\item this results in the orthonormal basis $A^*$ and a new projection matrix with $P_{m1}=a,~P_{m2}=b$.
\end{enumerate}
The random completion of $A$ outside the projection matrix provides an exploration of dimensions orthogonal to the projection plane. However, it renders projections in a way that is not continuouns and may be distracting. This can be alleviated by replacing the random completion with a rule restricting the size of the jumps.

@@

A very simple adjustment method works purely within the (hyper)plane, and is using the fact that the first direction will not be rotated when applying Gram-Schmidt. The following steps are needed:

1. Provide $A$, and $m$.
2. Change values in row $m$, giving $A^*$.
3. Rotate the basis within the projection (hyper-)plane, such that the first direction is aligned with the direction of $m$ in $A^*$, giving $\hat A^*$. In a 2D projection this means finding the angle $\theta$ by which the basis should be rotated.
4. Normalise the first direction in $\hat A^*$ while keeping the contribution in row $m$ fixed, giving $\hat A^{*0}$.
5. Orthonormalise $\hat A^{*0}$ using Gram-Schmidt, giving $\hat A^{**}$. By construction the contribution of $m$ will remain fixed.
6. Rotate $\hat A^{**}$ back into the original basis to obtain $A^{**}$.

@@

- **Why is this a good sandbox**
- **Explain the functionality available in the notebooks**

Here we describe the functions implemented in the Mathematica package `mmtour.wl`. The main function is

- `SliceDynamic[data, projmat, height, heightRange, legendQ(=1), flagQ(=1), colorFunc(=ColorData[97])]` with arguments

- `data`: A data matrix with an extra grouping that has a label (string) and a flag  (numerical) 
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `height`: The initial height of the slice.
- `heightRange`: The range of slice heights to be explored.
- `legendQ`: A flag signaling whether the data matrix includes a column with group labels (1) or not (0).
- `flagQ`: A flag signaling whether the data matrix includes a numerical flag for the groups.
- `colorFunc`: specifies the colour mapping for the different groups.

@@

This function can be used for ungrouped data setting  legendQ and flagQ to 0.

To remove a group from the visual display, the user can choose specific colours for the entry colorFunc. For example, {Red,White,Green} would display groups 1 (red) and 3 (green) while making 2 invisible.

Other functions are:

- `ProjectionPlot[data, projmat, legendNames(={}), colorFunc(=ColorData[97])]` with arguments

- `data`: A data matrix with one or more groups labeled by a flag  (numerical) 
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `legendNames`: an optional list of labels for the groups.
- `colorFunc`: specifies the colour mapping for the different groups.

This function is similar to SliceDynamic but can only display projections. Using it instead of SliceDynamic simplifies the display and is more efficient. The data file should not contain labels for groups, if these are desired they are passed through the optional argument legendNames as {"group 1", "group 2",...}, for example.

The display allows the user to navigate through different projections, choose the point size and zoom the factor, and explicitly display the coordinates of the projection.

- `ProjectedLocatorPlot[data, projmat, legendNames(={}), colorFunc(=ColorData[97])]` with arguments

- `data`: A data matrix with one or more groups labeled by a flag  (numerical) 
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `legendNames`: an optional list of labels for the groups.
- `colorFunc`: specifies the colour mapping for the different groups.

This function is very similar to ProjectionPlot but uses a different display for navigation of  projections in which each coordinate is represented on a separate dial.

- `VisualiseSliceDynamic[data, projmat, height, heightRange]` with arguments

- `data`: A data matrix containg only one set.In this case the data matrix should not contain column labels.
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `height`: The initial height of the slice.
- `heightRange`: The range of slice heights to be explored.

This function differs from SliceDynamic in that it looks at only one data set but displays both the points inside and outside the slice. The display panel allows the user to specify the size of both sets of points (inside and outside) along with the slice height, centre point and zoom level.

>>>>

A small modification to algorithm 1 will maintain the components of $V_m$ precisely (Figure \ref{fig:othermethod}). It is as follows:

@@

$$a^{**}_{j2}+\frac{a_{m1}a_{m2}}{p-1}, j=1, ..., p, j\neq m.$$

@@

$$\sum_{j=1, j\neq m}^p a^{**}_{j1}a^{**}_{j2} + a_{m1}a_{m2} = 0.$$

@@

\textcolor{red}{Notation does not match, everywhere else $A$ is the projection matrix onto 2d, so just the two columns, this is called $P$ here...maybe switch? $A$ can be considered as first two directions of the complete rotation matrix $P$?}

For $d=2$ projections, the projection matrix is the sub-matrix of $A$ formed by its first two columns. Whereas orthonormality of the basis for the p-dimensional space is given by $e_i\cdot e_j=\delta_{ij},{i,j,=1,\cdots, p}$, orthonormality of the projection matrix is expressed as $P_i\cdot P_j=\delta_{ij}, {i,j=1,2}$. Movement of the cursor takes the two components ${x_{m1},x_{m2}}$ into a selected new value ${a,b}$. Although the motion is constrained by $a^2+b^2\leq 1$, this is not sufficient to guarantee orthonormality of the new projection matrix. One possible algorithm to achieve this is
\begin{enumerate}
\item Cursor movement takes ${x_{m1},x_{m2}}\to {a,b}$
\item The freedom to change the components $A_{i3}\cdots A_{ip}$ (the columns of $A$ not corresponding to the projection matrix) is used to select a new orthonormal basis as follows:
\begin{enumerate}
\item For row $m$ one chooses $A_{m3}=\sqrt{1-a^2-b^2},~A_{m,k>3}=0$
\item For other rows, $A_{i\neq m,j\geq3}$ random selections in the range $(-1,1)$ are made.
\item The Gram-Schmidt algorithm is then used to obtain an orthonormal basis taking $e_m$ as the first vector (which is already normalized), and then proceeding as usual $e_1\to e_1-(e_1\cdot e_m) e_m$, $e_1\to e_1/(e_1\cdot e_1)$, etc.
\end{enumerate}
\item this results in the orthonormal basis $A^*$ and a new projection matrix with $P_{m1}=a,~P_{m2}=b$.
\end{enumerate}
The random completion of $A$ outside the projection matrix provides an exploration of dimensions orthogonal to the projection plane. However, it renders projections in a way that is not continuouns and may be distracting. This can be alleviated by replacing the random completion with a rule restricting the size of the jumps.

@@

Finally we may also consider an adjustment that works within the projection plane. The idea is that when applying Gram-Schmidt, the direction of the first basis vector is not changed. We thus rotate the projection matrix within the plane such that the first basis is aligned with the direction of the selected variable $m$ before applying orthonormalization. In addition we need to keep the contribution of variable $m$ along that direction fixed when normalizing the vector. The following steps are needed:

1. Provide $A$, and $m$.
2. Change values in row $m$, giving $A^*$.
3. Rotate the basis within the projection plane, such that the first basis direction is aligned with the direction of $m$ in $A^*$, giving $\hat A^*$. In a 2D projection this means finding the angle $\theta$ by which the basis should be rotated.
4. Normalize the first direction in $\hat A^*$ while keeping the contribution in row $m$ fixed, giving $\hat A^{*0}$.
5. Orthonormalize $\hat A^{*0}$ using Gram-Schmidt, giving $\hat A^{**}$. By construction the contribution of $m$ will remain fixed.
6. Rotate $\hat A^{**}$ back into the original basis to obtain $A^{**}$.

@@

Here we describe the functions implemented in the Mathematica package `mmtour.wl`. The main function and its arguments are given below:

`SliceDynamic[data, projmat, height, heightRange, legendQ(=1), flagQ(=1), colorFunc(=ColorData[97])]`

- `data`: A data matrix, potentially with grouping that has a label (string) and a flag  (numerical) in the last two columns.
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `height`: The initial height of the slice.
- `heightRange`: The range of slice heights to be explored.
- `legendQ`: A flag signaling whether the data matrix includes a column with group labels (1) or not (0).
- `flagQ`: A flag signaling whether the data matrix includes a numerical flag for the groups.
- `colorFunc`: specifies the colour mapping for the different groups.

\textcolor{red}{The first four arguments are required. As possible starting values we suggest using a random input projection, and selecting slice height parameters using the estimate given in Section 2.4.2 of the paper.}

@@

This function can be used for ungrouped data by setting legendQ and flagQ to 0.
To remove a group from the visual display, the user can choose specific colours for the entry colorFunc. For example, {Red,White,Green} would display groups 1 (red) and 3 (green) while making 2 invisible.

The Slice Tour* notebooks include the additional functions: `ProjectionPlot`, `Projected2DSliderPlot`, and `VisualiseSliceDyanmic`.

`ProjectionPlot` is very similar to `SliceDynamic`, except it only displays projections.
Using it instead of `SliceDynamic` simplifies the display and is more efficient. The interface is slightly different, the data file should not contain labels for groups, if these are desired they are passed through the optional argument legendNames as {"group 1", "group 2",...}, for example. The function and its arguments are given below:

`ProjectionPlot[data, projmat, legendNames(={}), colorFunc(=ColorData[97])]`

- `data`: A data matrix with one or more groups labeled by a flag (numerical, last column).
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `legendNames`: an optional list of labels for the groups.
- `colorFunc`: specifies the colour mapping for the different groups.

`ProjectedLocatorPlot` displays the interactive controls slightly differently. Several locator panes are displayed above the display of the projected data and each one corresponds to a row in the projection matrix. The updating behaviour of the projection is the same as in `ProjectionPlot`. The function and its arguments are given below:

`ProjectedLocatorPlot[data, projmat, legendNames(={}), colorFunc(=ColorData[97])]`

- `data`: A data matrix with one or more groups labeled by a flag  (numerical, last column). 
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `legendNames`: an optional list of labels for the groups.
- `colorFunc`: specifies the colour mapping for the different groups.

Finally `VisualiseSliceDynamic` allows to discern which points exist inside the slice and outside it. This function differs from `SliceDynamic` in that it looks at only one data set but displays both the points inside and outside the slice. The display panel allows the user to specify the size of both sets of points (inside and outside) along with the slice height, centre point and zoom level. The function and its arguments are given below:

`VisualiseSliceDynamic[data, projmat, height, heightRange]`

- `data`: A data matrix containing only one group. In this case the data matrix should not contain column labels.
- `projmat`: The initial projection matrix. It is possible to start with a random projection with the input "random" (including the quotes) in this entry field.
- `height`: The initial height of the slice.
- `heightRange`: The range of slice heights to be explored.

\textcolor{red}{How are they shown, different colors? Fading points that are outside?}

### 2022-09-22 paper/appendix.tex
Some work on the appendix

A small modification to algorithm 1 will maintain the components of
\(V_m\) precisely (Figure \ref{fig:othermethod}. It is as follows:

@@

\[a^{**}_{j2}+\frac{a_{m1}a_{m2}}{p-1}, j=1, ..., p, j\neq m\].

@@

\[\sum_{j=1, j\neq m}^p a^{**}_{j1}a^{**}_{j2} + a_{m1}a_{m2} = 0\].

@@

For \(d=2\) projections, the projection matrix is the sub-matrix of
\(A\) formed by its first two columns. Whereas orthonormality of the
basis for the p-dimensional space is given by
\(e_i\cdot e_j=\delta_{ij},{i,j,=1,\cdots,}\), orthonormality of the
projection matrix is expressed as
\(P_i\cdot P_j=\delta_{ij}, {i,j=1,2}\). Movement of the cursor takes
the two components \({x_{m1},x_{m2}}\) into a selected new value
\({a,b}\). Although the motion is constrained by \(a^2+b^2\leq 1\), this
is not sufficient to guarantee orthonormality of the new projection
matrix. One possible algorithm to achieve this is

@@

A very simple adjustment method works purely within the (hyper)plane,
and is using the fact that the first direction will not be rotated when
applying Gram-Schmidt. The following steps are needed:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Provide \(A\), and \(m\).
\item
  Change values in row \(m\), giving \(A^*\).
\item
  Rotate the basis within the projection (hyper-)plane, such that the
  first direction is aligned with the direction of \(m\) in \(A^*\),
  giving \(\hat A^*\). In a 2D projection this means finding the angle
  \(\theta\) by which the basis should be rotated.
\item
  Normalise the first direction in \(\hat A^*\) while keeping the
  contribution in row \(m\) fixed, giving \(\hat A^{*0}\).
\item
  Orthonormalise \(\hat A^{*0}\) using Gram-Schmidt, giving
  \(\hat A^{**}\). By construction the contribution of \(m\) will remain
  fixed.
\item
  Rotate \(\hat A^{**}\) back into the original basis to obtain
  \(A^{**}\).
\end{enumerate}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Why is this a good sandbox}
\item
  \textbf{Explain the functionality available in the notebooks}
\end{itemize}

Here we describe the functions implemented in the Mathematica package
\texttt{mmtour.wl}. The main function is

\begin{itemize}
\item
  \texttt{SliceDynamic{[}data,\ projmat,\ height,\ heightRange,\ legendQ(=1),\ flagQ(=1),\ colorFunc(=ColorData{[}97{]}){]}}
  with arguments
\item
  \texttt{data}: A data matrix with an extra grouping that has a label
  (string) and a flag (numerical)
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{height}: The initial height of the slice.
\item
  \texttt{heightRange}: The range of slice heights to be explored.
\item
  \texttt{legendQ}: A flag signaling whether the data matrix includes a
  column with group labels (1) or not (0).
\item
  \texttt{flagQ}: A flag signaling whether the data matrix includes a
  numerical flag for the groups.
\item
  \texttt{colorFunc}: specifies the colour mapping for the different
  groups.
\end{itemize}

@@

This function can be used for ungrouped data setting legendQ and flagQ
to 0.

To remove a group from the visual display, the user can choose specific
colours for the entry colorFunc. For example, \{Red,White,Green\} would
display groups 1 (red) and 3 (green) while making 2 invisible.

Other functions are:

\begin{itemize}
\item
  \texttt{ProjectionPlot{[}data,\ projmat,\ legendNames(=\{\}),\ colorFunc(=ColorData{[}97{]}){]}}
  with arguments
\item
  \texttt{data}: A data matrix with one or more groups labeled by a flag
  (numerical)
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{legendNames}: an optional list of labels for the groups.
\item
  \texttt{colorFunc}: specifies the colour mapping for the different
  groups.
\end{itemize}

This function is similar to SliceDynamic but can only display
projections. Using it instead of SliceDynamic simplifies the display and
is more efficient. The data file should not contain labels for groups,
if these are desired they are passed through the optional argument
legendNames as \{``group 1'', ``group 2'',\ldots\}, for example.

The display allows the user to navigate through different projections,
choose the point size and zoom the factor, and explicitly display the
coordinates of the projection.

\begin{itemize}
\item
  \texttt{ProjectedLocatorPlot{[}data,\ projmat,\ legendNames(=\{\}),\ colorFunc(=ColorData{[}97{]}){]}}
  with arguments
\item
  \texttt{data}: A data matrix with one or more groups labeled by a flag
  (numerical)
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{legendNames}: an optional list of labels for the groups.
\item
  \texttt{colorFunc}: specifies the colour mapping for the different
  groups.
\end{itemize}

This function is very similar to ProjectionPlot but uses a different
display for navigation of projections in which each coordinate is
represented on a separate dial.

\begin{itemize}
\item
  \texttt{VisualiseSliceDynamic{[}data,\ projmat,\ height,\ heightRange{]}}
  with arguments
\item
  \texttt{data}: A data matrix containg only one set.In this case the
  data matrix should not contain column labels.
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{height}: The initial height of the slice.
\item
  \texttt{heightRange}: The range of slice heights to be explored.
\end{itemize}

This function differs from SliceDynamic in that it looks at only one
data set but displays both the points inside and outside the slice. The
display panel allows the user to specify the size of both sets of points
(inside and outside) along with the slice height, centre point and zoom
level.

>>>>

A small modification to algorithm 1 will maintain the components of
\(V_m\) precisely (Figure \ref{fig:othermethod}). It is as follows:

@@

\[a^{**}_{j2}+\frac{a_{m1}a_{m2}}{p-1}, j=1, ..., p, j\neq m.\]

@@

\[\sum_{j=1, j\neq m}^p a^{**}_{j1}a^{**}_{j2} + a_{m1}a_{m2} = 0.\]

@@

\textcolor{red}{Notation does not match, everywhere else $A$ is the projection matrix onto 2d, so just the two columns, this is called $P$ here...maybe switch? $A$ can be considered as first two directions of the complete rotation matrix $P$?}

For \(d=2\) projections, the projection matrix is the sub-matrix of
\(A\) formed by its first two columns. Whereas orthonormality of the
basis for the p-dimensional space is given by
\(e_i\cdot e_j=\delta_{ij},{i,j,=1,\cdots, p}\), orthonormality of the
projection matrix is expressed as
\(P_i\cdot P_j=\delta_{ij}, {i,j=1,2}\). Movement of the cursor takes
the two components \({x_{m1},x_{m2}}\) into a selected new value
\({a,b}\). Although the motion is constrained by \(a^2+b^2\leq 1\), this
is not sufficient to guarantee orthonormality of the new projection
matrix. One possible algorithm to achieve this is

@@

Finally we may also consider an adjustment that works within the
projection plane. The idea is that when applying Gram-Schmidt, the
direction of the first basis vector is not changed. We thus rotate the
projection matrix within the plane such that the first basis is aligned
with the direction of the selected variable \(m\) before applying
orthonormalization. In addition we need to keep the contribution of
variable \(m\) along that direction fixed when normalizing the vector.
The following steps are needed:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Provide \(A\), and \(m\).
\item
  Change values in row \(m\), giving \(A^*\).
\item
  Rotate the basis within the projection plane, such that the first
  basis direction is aligned with the direction of \(m\) in \(A^*\),
  giving \(\hat A^*\). In a 2D projection this means finding the angle
  \(\theta\) by which the basis should be rotated.
\item
  Normalize the first direction in \(\hat A^*\) while keeping the
  contribution in row \(m\) fixed, giving \(\hat A^{*0}\).
\item
  Orthonormalize \(\hat A^{*0}\) using Gram-Schmidt, giving
  \(\hat A^{**}\). By construction the contribution of \(m\) will remain
  fixed.
\item
  Rotate \(\hat A^{**}\) back into the original basis to obtain
  \(A^{**}\).
\end{enumerate}

@@

Here we describe the functions implemented in the Mathematica package
\texttt{mmtour.wl}. The main function and its arguments are given below:

\texttt{SliceDynamic{[}data,\ projmat,\ height,\ heightRange,\ legendQ(=1),\ flagQ(=1),\ colorFunc(=ColorData{[}97{]}){]}}

\begin{itemize}
\tightlist
\item
  \texttt{data}: A data matrix, potentially with grouping that has a
  label (string) and a flag (numerical) in the last two columns.
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{height}: The initial height of the slice.
\item
  \texttt{heightRange}: The range of slice heights to be explored.
\item
  \texttt{legendQ}: A flag signaling whether the data matrix includes a
  column with group labels (1) or not (0).
\item
  \texttt{flagQ}: A flag signaling whether the data matrix includes a
  numerical flag for the groups.
\item
  \texttt{colorFunc}: specifies the colour mapping for the different
  groups.
\end{itemize}

\textcolor{red}{The first four arguments are required. As possible starting values we suggest using a random input projection, and selecting slice height parameters using the estimate given in Section 2.4.2 of the paper.}

@@

This function can be used for ungrouped data by setting legendQ and
flagQ to 0. To remove a group from the visual display, the user can
choose specific colours for the entry colorFunc. For example,
\{Red,White,Green\} would display groups 1 (red) and 3 (green) while
making 2 invisible.

The Slice Tour* notebooks include the additional functions:
\texttt{ProjectionPlot}, \texttt{Projected2DSliderPlot}, and
\texttt{VisualiseSliceDyanmic}.

\texttt{ProjectionPlot} is very similar to \texttt{SliceDynamic}, except
it only displays projections. Using it instead of \texttt{SliceDynamic}
simplifies the display and is more efficient. The interface is slightly
different, the data file should not contain labels for groups, if these
are desired they are passed through the optional argument legendNames as
\{``group 1'', ``group 2'',\ldots\}, for example. The function and its
arguments are given below:

\texttt{ProjectionPlot{[}data,\ projmat,\ legendNames(=\{\}),\ colorFunc(=ColorData{[}97{]}){]}}

\begin{itemize}
\tightlist
\item
  \texttt{data}: A data matrix with one or more groups labeled by a flag
  (numerical, last column).
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{legendNames}: an optional list of labels for the groups.
\item
  \texttt{colorFunc}: specifies the colour mapping for the different
  groups.
\end{itemize}

\texttt{ProjectedLocatorPlot} displays the interactive controls slightly
differently. Several locator panes are displayed above the display of
the projected data and each one corresponds to a row in the projection
matrix. The updating behaviour of the projection is the same as in
\texttt{ProjectionPlot}. The function and its arguments are given below:

\texttt{ProjectedLocatorPlot{[}data,\ projmat,\ legendNames(=\{\}),\ colorFunc(=ColorData{[}97{]}){]}}

\begin{itemize}
\tightlist
\item
  \texttt{data}: A data matrix with one or more groups labeled by a flag
  (numerical, last column).
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{legendNames}: an optional list of labels for the groups.
\item
  \texttt{colorFunc}: specifies the colour mapping for the different
  groups.
\end{itemize}

Finally \texttt{VisualiseSliceDynamic} allows to discern which points
exist inside the slice and outside it. This function differs from
\texttt{SliceDynamic} in that it looks at only one data set but displays
both the points inside and outside the slice. The display panel allows
the user to specify the size of both sets of points (inside and outside)
along with the slice height, centre point and zoom level. The function
and its arguments are given below:

\texttt{VisualiseSliceDynamic{[}data,\ projmat,\ height,\ heightRange{]}}

\begin{itemize}
\tightlist
\item
  \texttt{data}: A data matrix containing only one group. In this case
  the data matrix should not contain column labels.
\item
  \texttt{projmat}: The initial projection matrix. It is possible to
  start with a random projection with the input ``random'' (including
  the quotes) in this entry field.
\item
  \texttt{height}: The initial height of the slice.
\item
  \texttt{heightRange}: The range of slice heights to be explored.
\end{itemize}

\textcolor{red}{How are they shown, different colors? Fading points that are outside?}
